\input{thispreamble.tex}

\input{preamble-instructions.tex}

\begin{center}
  \textsc{Honor Statement}
\end{center}
I, \answerbox{Carl Alexander Dalebout},
attest to the fact that the submitted work is my own and
is not the result of plagiarism.
Furthermore, I have not aided another student in the act of
plagiarism.

\input{preamble.tex}

\newpage
Q1. \input{q1.tex}

\textsc{Answer}
\begin{answercode}
  select eid from Certified where aid in 
  (select aid from Aircraft where aname = "Flight Crew Shuttle");
\end{answercode}

Q2. \input{q2.tex}

\textsc{Answer}
\begin{answercode}
  select ename from Employee where eid in
  (select eid from Certified where aid in 
  (select aid from Aircraft where aname = "Flight Crew Shuttle"));
\end{answercode}

Q3. \input{q3.tex}

\textsc{Answer}
\begin{answercode}
  select aid from Aircraft where cruisingrange in
  (select distance from Flights where 
    from = "begger's Canyon" and to = "Dune Sea Exchange");
\end{answercode}


\newpage
Q4. \input{q4.tex}

\textsc{Answer}
\begin{answercode}
select aid from Aircraft where eid in 
(select eid from Employee where salery > 100);
\end{answercode}


\newpage

Q5. \input{q5.tex}

\textsc{Answer}
\begin{answercode}
select ename from Employee where eid in
(select eid from Certified where aid in 
(select aid from Aircraft where 
  aname != "Flight Crew Shuttle" and cruisingrange > 2000));
\end{answercode}


Q6. \input{q6.tex}

\textsc{Answer}
\begin{answercode}
select eid, MAX(salary) from Employee;
\end{answercode}

\newpage

Q7. \input{q7.tex}

\textsc{Answer}
\begin{answercode}
  select eid, MAX(salary) from Employee where 
  salary not in (select MAX(salary) from Employee);
\end{answercode}


Q8. \input{q8.tex}

\textsc{Answer}
\begin{answercode}
select eid, Max(count(eid)) as certifications from Certified group by eid
\end{answercode}


\newpage
Q9. \input{q9.tex}

\textsc{Answer}
\begin{answercode}
create temporary table temp
(
  select eid, count(eid) as certifications from Certified group by eid
);

select eid from Certified where certifications = 3 in temp;
\end{answercode}


Q10. \input{q10.tex}

\textsc{Answer}
\begin{answercode}
select SUM(salary) from Employee;
\end{answercode}


\newpage
Q11. \input{q11.tex}

\textsc{Answer}
\begin{answercode}
  with recursive paths (end, path) as
  (
    select to, convert(to, varchar(1024)) -- note: type of path is
      from Flights
      where from is "Raider Camp"
    union all
    select t.to, concat(p.path, ',', t.to)
      from paths as p, Flights as t
      where t.to = "Rebel Depot"
  )
  select * from paths;
  
\end{answercode}


\newpage
\input{supportticket.tex}


\newpage
\input{q12.tex}

\textsc{Answer}
\begin{answercode}
Null

The reason being is becuase in sql you would not be able 
to create a table that would be able to calculate the 
wait time of a single ticket let alone all of them.
\end{answercode}




\newpage
\input{q13.tex}

\textsc{Answer}
\begin{answercode}

\end{answercode}


\newpage
Q12. \input{q14.tex}

\textsc{Answer}
\begin{answercode}

\end{answercode}

\end{document}
